\documentclass[12pt,-letter paper]{article}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\begin{document}
\begin{enumerate}
\section*{\centering MATHEMATICS}
		\section*{\centering QUESTIONS}
	\item Write the value of $\mydet{a-b&b-c&c-a\\b-c&c-a&a-b\\c-a&a-b&b-c}$.

	\item If $\vec{A}=\myvec{1&-2&3\\-4&2&5}$and $\vec{B}$=$\myvec{2&3\\4&5\\2&1}$ and BA=\brak{bij},find $b_{21}$+$b_{32}i$.

\item Write the number of all the possible matrices of order $2\times3$ with each entry $1$ or $2$.

\item Write the coordinates of the point which is the reflection of the point $(\alpha,\beta,\gamma)$ in the XZ-plane.

\item Find the position vector of the point which divides the join of points with position vectors $\overset{\rightarrow}{a}+3\overset{\rightarrow}{b} and \overset{\rightarrow}{a}-\overset{\rightarrow}{b}$ in the ratio $1:3$.
\item If $\mydet{\overset{\rightarrow}{a}}=4,\mydet{\overset{\rightarrow}{b}}=3$ and $\overset{\rightarrow}{a}\cdot\overset{\rightarrow}{b}=6\sqrt{3}$,then find the value of $\mydet{\overset{\rightarrow}{a}\times\overset{\rightarrow}{b}}$.

\item Solve for $x:tan^{-1}\brak{\frac{2-x}{2+x}}$=$\brak{\frac{1}{2}}tan^{-1}\brak{\frac{x}{2}}$,$x \textgreater 0$.
	
\item Prove that $2sin^{-1}\brak{\frac{3}{5}}-tan^{-1}\brak{\frac{17}{31}}=\brak{\frac{\pi}{4}}$.
\item On her birthday Seema decided to donate some money to chldren of an rophanage home.If there was 8 children less,everyone would have go \rupee $10$ more.However,if there were $16$ children more,every one would have got\rupee $10$ less.Using matrix method,find the numbers of children and the amount distributed by Seema.What values are refleced by Seema's decision?
\item If $x=e^{cos2t}$ and $y=e^{sin2t}$,prove that $\frac{dy}{dx}$=$\frac{-y}{x}$ $\frac{logx}{logy}$.\\ Verify mean value theorem for the function $f(x)=2sinx+sin2x$ on $[o,x]$.
\item Find the eqation of the tangent line to the curve $y={\sqrt5x-3}{-5}$,when parallel to the line $4x-2y=5=0$.
\item Show that the function $f$ given by fx=$\begin{cases}\frac{e^{\frac{1}{x}}-1}{e^{\frac{1}{x}}+1},& if x\neq0\\
$-1$,& if x=0 \end{cases}$ \\is discontinuous at $x=0$. 
\item Evaluate: $\int_{1}^{5}$ $\{|x-1| + |x-2| + |x-3|\}$dx.
		\item Evaluate: $\int_{0}^{\pi} \frac{xsinx}{1+3cos^2x}dx$.
		\item Find: $\int\frac{2x+1}{\brak{x^2}\brak{x^2}}$dx.
		\item Find $\int \brak{3x+5}$ $\sqrt{5x+4x-2x^2}$dx.
	\item x$\frac{dy}{dx}+y-x+xycotx=0$;$x\neq0$.
	\item Solve the different equation:$\brak{x^2+3xy+y^2}dx$ $-x^2dy=0$ given that $y=0$,when $x=1$.
	\item Find the angle between the vectors $\overset{\rightarrow}{a}+\overset{\rightarrow}{b}$ and $\overset{\rightarrow}{a}-\overset{\rightarrow}{b}$ if $\overset{\rightarrow}{a}=2\hat{i}-\hat{j}+3\hat{k}$ and $\overset{\rightarrow}{b}=3\hat{i}+\hat{j}-2\hat{k}$,and hence find a vector perpendicular to both $\overset{\rightarrow}{a}+\overset{\rightarrow}{b}$ and $\overset{\rightarrow}{a}-\overset{\rightarrow}{b}$.
	\item Show that the line $\frac{x-1}{3}=\frac{y-1}{-1}=\frac{z+1}{0}$ and $\frac{x-4}{2}=\frac{y}{0}=\frac{z+1}{3}$ intersect.Find their point of intersection.
	\item A committee of $4$ students is selected at random from a group consisting of $7$ boys and $4$ girls. Find the probability that there are exactly $2$ boys in the committee, given that at least one girl must be there in the committee.
	\item Show that the relation R defined by \brak{a,b}R\brak{c,d}$\Rightarrow a+d=b+c$ on the $A\times A$,where $A=\{1,2,3,...10\}$ is an equivalence class $\myvec{\brak{3,4}};a,b,c,d \epsilon A$.
		\item Solve for x: $\mydet{a+x&a-x&a-x\\a-x&a+x&a-x\\a-x&a-x&a+x}=0$,\\
		 using properties of determinants.
	 \item Using elementary row operation find the inverse of matrix X $\vec{A}\myvec{3&-3&4\\
			 2&-3&4\\
			 0&-1&1\\}$ and hence solve the following system of equations $3x-3y+4z=21,2x-3y+4z=20,-y+z=5$.
	 \item Show that height of the cylinder of greatest volume which can be in scribed in aright circular cone of height h and semi-vertical angle $\alpha$ is one third that of and greatest volume of cylinder is $\frac{4}{27}\pi \tan^2 \alpha$.
		 \item Find the intervals in which the function $f(x)=\frac{4sinx}{2+cosx}-x;0\leq x \leq 2\pi$ is strictly increasing or strictly decreasing.
		 \item Using integration,find the area of the triangle formed by inegative x-axis and tangent and normal to the circle $x^2+y^2=9$ at $\brak{-1,2\sqrt{2}}$.
	 \item Find the coordinates of the foot of perpendicular distance frm the point P $\brak{4,3,2}$ to the plane $x+2y+3z=2$.Also find the image of P in the plane.
	 \item $A$, B and C throw a pair of dice in that order alternately till one of them gets a total of $9$ and wins the game. Find their respective probabilities of winning, if A starts first.
	 \item A company manufactures two types of cardigans type A and type B. It costs \rupee $360$ to make a type A cardigan and \rupee $120$ to make a type B cardigan. The company can make at most $300$ cardigans and spend at most \rupee $72,000$ a day. The number of cardigans of type B cannot exceed the number of cardigans of type A by more than \rupee $200$. The company makes a profit of \rupee $100$ for each cardigan of type A and \rupee $50$ for every cardigan of type B.\\

Formulate this problem as a linear programming problem to maximise the profit to the company. Solve it graphically and find maximum profit.
\end{enumerate}
\end{document}

