\documentclass[12pt,-letter paper]{article}
\usepackage{gvv}
\usepackage{amsmath}
\begin{document}
\begin{enumerate}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}

\section*{\centering MATHEMATICS}
		\section*{\centering QUESTIONS}
	\item Write the value of $\mydet{a-b&b-c&c-a\\b-c&c-a&a-b\\c-a&a-b&b-c}$.

	\item If $\vec{A}=\myvec{1&-2&3\\-4&2&5}$and $\vec{B}$=$\myvec{2&3\\4&5\\2&1}$ and $BA=\brak{bij}$,find $b_{21}$+$b_{32}i$.

\item Write the number of all the possible matrices of order $2\times3$ with each entry $1$ or $2$.

\item Write the coordinates of the point which is the reflection of the point $(\alpha,\beta,\gamma)$ in the XZ-plane.

\item Find the position vector of the point which divides the join of points with position vectors $\vec{a}+3\vec{b} and \vec{a}-\vec{b}$ in the ratio .

\item If $\mydet{\vec{a}}=4,\mydet{\vec{b}}=3$ and $\vec{a}\cdot\vec{b}=6\sqrt{3}$,then find the value of $\mydet{\vec{a}\times\vec{b}}$.

\item Solve for \begin{align} x:\tan^{-1}\brak{\frac{2-x}{2+x}}=\brak{\frac{1}{2}}\tan^{-1}\brak{\frac{x}{2}},x \textgreater 0\end{align}.
	
	\item Prove that \begin{align}2\sin^{-1}\brak{\frac{3}{5}}-\tan^{-1}\brak{\frac{17}{31}}=\brak{\frac{\pi}{4}}\end{align}.
\item On her birthday Seema decided to donate some money to chldren of an rophanage home.If there was $8$ children less,everyone would have go \rupee $10$ more.However,if there were $16$ children more,every one would have got\rupee $10$ less.Using matrix method,find the numbers of children and the amount distributed by Seema.What values are refleced by Seema's decision?
\item If \begin{align}x=e^{\cos2t} and y=e^{\sin2t}\end{align},prove that \begin{align}\frac{dy}{dx}=\frac{-y}{x} \frac{logx}{logy}\end{align}. Verify mean value theorem for the function \begin{align}f(x)=2s\in x+\sin2x \end{align}.
	\item Find the eqation of the tangent line to the curve \begin{align}y={\sqrt5x-3}{-5}\end{align},when parallel to the line \begin{align}4x-2y=5=0\end{align} .
		\item Show that the function $f$ given by $fx$=$\begin{cases}\frac{e^{\frac{1}{x}}-1}{e^{\frac{1}{x}}+1},& \text if x\neq0\\ -1,& \text if x=0 \end{cases}$ is discontinuous . 
				\item Evaluate: \begin{align}\int_{1}^{5} \{\mydet{x-1} + \mydet{x-2} + \mydet{x-3}\}dx\end{align}.
					\item Evaluate: \begin{align}\int_{0}^{\pi} \frac{x\sin x}{1+3\cos^2x}dx\end{align}.
						\item Find: \begin{align}\int\frac{2x+1}{\brak{x^2}\brak{x^2}}dx\end{align}.
							\item Find \begin{align}\int \brak{3x+5} \sqrt{5x+4x-2x^2}dx\end{align} .
								\item x \begin{align}\frac{dy}{dx}+y-x+xycotx=0;x\neq0\end{align}.
									\item Solve the different equation:\begin{align}\brak{x^2+3xy+y^2}dx -x^2dy=0\end{align} given that \begin{align}\text y=0,when x=1\end{align}.
										\item Find the angle between the vectors \begin{align}\vec{a}+\vec{b} \text and \vec{a}-\vec{b} \text if \vec{a}=2\hat{i}-\hat{j}+3\hat{k} \text and \vec{b}=3\hat{i}+\hat{j}-2\hat{k}\end{align},and hence find a vector perpendicular to both \begin{align}\vec{a}+\vec{b} \text and \vec{a}-\vec{b}\end{align}.
	\item Show that the line \begin{align}\frac{x-1}{3}=\frac{y-1}{-1}=\frac{z+1}{0}\end{align} \text and \begin{align}\frac{x-4}{2}=\frac{y}{0}=\frac{z+1}{3}\end{align} intersect.Find their point of intersection.
	\item A committee of $4$ students is selected at random from a group consisting of $7$ boys and $4$ girls. Find the probability that there are exactly $2$ boys in the committee, given that at least one girl must be there in the committee.
	\item Show that the relation $R$ defined by \begin{align}\brak{a,b}R\brak{c,d}\Rightarrow a+d=b+c\end{align} on the $A\times A$,where \begin{align}A=\{1,2,3,...10\}\end{align} is an equivalence class $\myvec{\brak{3,4}};a,b,c,d \epsilon A$.
		\item Solve for x: $\mydet{a+x&a-x&a-x\\a-x&a+x&a-x\\a-x&a-x&a+x}=0$, using properties of determinants.
	 \item Using elementary row operation find the inverse of matrix X $\vec{A}\myvec{3&-3&4\\
			 2&-3&4\\
			 0&-1&1\\}$ and hence solve the following system of equations \begin{align}3x-3y+4z=21\\2x-3y+4z=20\\-y+z=5\end{align}.
			 \item Show that height of the cylinder of greatest volume which can be in scribed in aright circular cone of height h and semi-vertical angle $\alpha$ is one third that of and greatest volume of cylinder is \begin{align}\frac{4}{27}\pi \tan^2 \alpha\end{align}.
				 \item Find the intervals in which the function \begin{align}f(x)=\frac{4\sin x}{2+\cos x}-x;0\leq x \leq 2\pi\end{align} is strictly increasing or strictly decreasing.
					 \item Using integration,find the area of the triangle formed by inegative x-axis and tangent and normal to the circle \begin{align}x^2+y^2=9 \text at \brak{-1,2\sqrt{2}} \end{align}.
						 \item Find the coordinates of the foot of perpendicular distance frm the point P $\brak{4,3,2}$ to the plane \begin{align}x+2y+3z=2\end{align}.Also find the image of $P$ in the plane.
	 \item $A$, $B$ and $C$ throw a pair of dice in that order alternately till one of them gets a total of $9$ and wins the game. Find their respective probabilities of winning, if $A$ starts first.
	 \item A company manufactures two types of cardigans type $A$ and type $B$. It costs \rupee $360$ to make a type $A$ cardigan and \rupee $120$ to make a type $B$ cardigan. The company can make at most $300$ cardigans and spend at most \rupee $72,000$ a day. The number of cardigans of type $B$ cannot exceed the number of cardigans of type $A$ by more than \rupee $200$. The company makes a profit of \rupee $100$ for each cardigan of type $A$ and \rupee $50$ for every cardigan of type $B$ .

Formulate this problem as a linear programming problem to maximise the profit to the company. Solve it graphically and find maximum profit.
\end{enumerate}
\end{document}

